---
title: "Analyses"
author: "Steve Brunwasser"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
    toc_depth: '2'
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    code_folding: hide
    theme: cosmo
    highlight: tango
---



```{r}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

# Prepare Workspace

Load packages
```{r}
require( robumeta )
require( Hmisc )
require( ggplot2 )
```


Load the data frame
```{r}
load( 'dfsub.RData' )
```

<br>

# Descriptives

Look at the descriptive statistics for the key modeling variables
```{r}
dfsub1 <- dfsub[, c('es','es.se','exp.012','mingen','hosp' ) ]
dfsub1$loges <- log( dfsub1$es )
label( dfsub1$loges ) <- 'Effect estimate on log scale'
label( dfsub1$es ) <- 'Effect estimate on linear scale'
label( dfsub1$es.se ) <- 'Standard error of log effect estimate'
html( describe( dfsub1 ) )
```

<br<

Plot the effect estimates on the log scale
```{r}
dfsub$w <- 1/dfsub$es.se
qqplot <- ggplot( dfsub, aes( sample = log( es ) ) ) +
  stat_qq(  ) +
  stat_qq_line( )
qqplot
```

<br>

# Analyses

## Marginal model
Run an intercept-only model, providing just a marginal weighted mean effect size.
```{r}
m1 <- robu( log( es ) ~ 1, 
            studynum = record_id, 
            var.eff.size = es.se^2,
            data = dfsub,
            modelweights = 'CORR',
            small = T,
            rho=.8
            )
print( m1 )
```


Anti-log the estimate and confidence intervals to get odds ratios
```{r}
( model1.eff <- data.frame( OddsRatioEstimate=round( exp( m1$reg_table$b.r ), digits = 2 ), 
                           LCI=round( exp( m1$reg_table$CI.L ), digits = 2 ),
                           UCI=round( exp( m1$reg_table$CI.U ), digits = 2 ) 
                           ) 
  )

#save(model1.eff, file='model1.eff.RData')
```

Marginal weighted mean effect estimates ($OR_+$) compatible with our data range from 0.58 (lower bound 95% CI) to 0.90 (upper bound 95% CI) with a point estimate of $OR_+=0.72$. Having an RSV LRTI relative to non-RSV LRTI is associated with a 10-42% reduction in odds for subsequent wheezing illness. An increase in the odds of subsequent wheezing illness with RSV LRTI vs. non-RSV LRTI is not compatible with our data with $\alpha=.05$. 

<br>

Conduct a sensitivity analysis to see if selection of values of $\rho$ (an estimate of the within study correlation among effect sizes) alters the results in any meaningful way. (Specification of a value for $\rho$ is needed to calculate efficient weights.)

```{r}
sensitivity( m1 )
```
We see that the value of $\rho$, whether it is 0 or 1, makes no meaningful difference in estimates of coefficients, standard errors, or $\tau^2$.

<br>

# Adjusted model

Add predictors coding whether studies limited exposure ascertainment to the first year of life (**exp.012**), adjusted for genetic confounding (**mingen**), and whether hospitalization/emergency care was required for LRTI exposure (**hosp**). The intercept of this model is the weighed mean effect size when all covariates are held at their reference values representing the modal (most common) level. 

```{r}
m2 <- robu( log( es ) ~ exp.012 + mingen + relevel( hosp, ref = 'Emergency/Hospitalization Required'), 
            studynum = record_id, 
            var.eff.size = es.se^2,
            data = dfsub,
            modelweights = 'CORR',
            small = T
            )
options( digits = 2 )
print( m2 )

```


```{r}
( model2.eff <- data.frame( Predictor=c('Intercept','Exposure Ascertainment Period','Genetic Adjustment','Emergency Care or Hospitalization Required'),
                           df= m2$reg_table$dfs, 
                           OR=round( exp( m2$reg_table$b.r ), digits = 2 ), 
                           LCI=round( exp( m2$reg_table$CI.L ), digits = 2 ),
                           UCI=round( exp( m2$reg_table$CI.U ), digits = 2 )
                           )
  )

save( model2.eff, file='model2.eff.RData')
```

The adjusted weighted mean odds ratio, holding all covariates at their modal levels, was $OR_+=0.60$ with values from 0.45 to 0.81 compatible with our data. There is insufficient evidence that any of the covariates modify the effects of RSV LRTI vs non-RSV LRTI on subsequent wheezing illness. 
`
<br>

Again, we see from the sensitivity analysis below that the value of $\rho$ provided in the analysis makes no practical difference.


```{r}
sensitivity( m2 )
```
```



```{r}
m2a <- robu( log( es ) ~ relevel( exp.012, ref = 'Limited to first year of life')  + mingen + relevel( hosp, ref = 'Emergency/Hospitalization Required'), 
            studynum = record_id, 
            var.eff.size = es.se^2,
            data = dfsub,
            modelweights = 'CORR',
            small = T
            )
print( m2a )
```



```{r}
( model2a.eff <- data.frame( OddsRatioEstimate=round( exp( m2a$reg_table$b.r ), digits = 2 ), 
                           LCI=round( exp( m2a$reg_table$CI.L ), digits = 2 ),
                           UCI=round( exp( m2a$reg_table$CI.U ), digits = 2 ),
                           Predictor=c('Intercept','Exposure Period','Genetic Adjustment','Emergency/Hospitalization')
                           ) 
  )

save( model2a.eff, file='model2a.eff.RData')

```
