---
title: "DataPrep"
author: "Steve Brunwasser"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    code_folding: hide
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

# Workspace Preparation

Read in data file
```{r}
df <- read.csv( 'WHORSVAsthmaReview_DATA_2022-07-27_0856.csv', header = T )
```

Create study-level data frame
```{r}
study <- df[, c(1:35, 740:747 ) ]
```

# Outcome 1 preparation

Create outcome 1 data frame
```{r}
out1 <- df[, c( 1, 36:84 ) ]
```

Create outcome 1, comparison 1 data frame
```{r}
out1comp1 <- df[, c( 1, 85:137 ) ]

out1comp1$out1comp1expmeth___6 <- NULL

out1comp1.long <- reshape( out1comp1,
                           varying = list( estype = c('out1comp1time1estype','out1comp1time2estype','out1comp1time3estype'),
                                           esdesc = c('out1comp1time1esdesc','out1comp1time2esdesc','out1comp1time3esdesc'),
                                           esmethod = c('out1comp1time1esmethod','out1comp1time2esmethod','out1comp1time3esmethod'),
                                           es = c('es_out1comp1time1','es_out1comp1time2','es_out1comp1time3'),
                                           es.se.report = c('es_se_report_o1c1t1','es_se_report_o1c1t2','es_se_report_o1c1t3'),
                                           es.se = c( 'es_se_o1c1t1','es_se_o1c1t2','es_se_o1c1t3'),
                                           n = c('es_out1comp1time1n','es_out1comp1time2n','es_out1comp1time3n'),
                                           expevent = c('out1comp1time1expevent','out1comp1time2expevent','out1comp1time3expevent'),
                                           expnonevent = c('out1comp1time1expnon','out1comp1time2expnon','out1comp1time3expnon'),
                                           compevent = c( 'out1comp1time1compevent','out1comp1time2compevent','out1comp1time3compevent'),
                                           compnonevent = c( 'out1comp1time1compnon','out1comp1time2compnon','out1comp1time3compnon'),
                                           outage = c( 'es_out1comp1time1age','es_out1comp1time2age','es_out1comp1time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out1comp1.long1 <- out1comp1.long[ order( out1comp1.long$record_id, out1comp1.long$time ), ]
out1comp1.long1$comparison <- 1        

out1comp1.long1$out1comp1expmeth___6 <- NULL
```

Create outcome 1, comparison 2 data frame
```{r}
out1comp2 <- df[, c( 1, 139:190 ) ]
out1comp2.long <- reshape( out1comp2,
                           varying = list( estype = c('out1comp2time1estype','out1comp2time2estype','out1comp2time3estype'),
                                           esdesc = c('out1comp2time1esdesc','out1comp2time2esdesc','out1comp2time3esdesc'),
                                           esmethod = c('out1comp2time1esmethod','out1comp2time2esmethod','out1comp2time3esmethod'),
                                           es = c('es_out1comp2time1','es_out1comp2time2','es_out1comp2time3'),
                                           es.se.report = c('es_se_report_o1c2t1','es_se_report_o1c2t2','es_se_report_o1c2t3'),
                                           es.se = c( 'es_se_o1c2t1','es_se_o1c2t2','es_se_o1c2t3'),
                                           n = c('es_out1comp2time1n','es_out1comp2time2n','es_out1comp2time3n'),
                                           expevent = c('out1comp2time1expevent','out1comp2time2expevent','out1comp2time3expevent'),
                                           expnonevent = c('out1comp2time1expnon','out1comp2time2expnon','out1comp2time3expnon'),
                                           compevent = c( 'out1comp2time1compevent','out1comp2time2compevent','out1comp2time3compevent'),
                                           compnonevent = c( 'out1comp2time1compnon','out1comp2time2compnon','out1comp2time3compnon'),
                                           outage = c( 'es_out1comp2time1age','es_out1comp2time2age','es_out1comp2time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out1comp2.long1 <- out1comp2.long[ order( out1comp2.long$record_id, out1comp2.long$time ), ]
out1comp2.long1$comparison <- 2      
```

Create outcome 1, comparison 3 data frame
```{r}
out1comp3 <- df[, c( 1, 192:243 ) ]

out1comp3.long <- reshape( out1comp3,
                           varying = list( estype = c('out1comp3time1estype','out1comp3time2estype','out1comp3time3estype'),
                                           esdesc = c('out1comp3time1esdesc','out1comp3time2esdesc','out1comp3time3esdesc'),
                                           esmethod = c('out1comp3time1esmethod','out1comp3time2esmethod','out1comp3time3esmethod'),
                                           es = c('es_out1comp3time1','es_out1comp3time2','es_out1comp3time3'),
                                           es.se.report = c('es_se_report_o1c3t1','es_se_report_o1c3t2','es_se_report_o1c3t3'),
                                           es.se = c( 'es_se_o1c3t1','es_se_o1c3t2','es_se_o1c3t3'),
                                           n = c('es_out1comp3time1n','es_out1comp3time2n','es_out1comp3time3n'),
                                           expevent = c('out1comp3time1expevent','out1comp3time2expevent','out1comp3time3expevent'),
                                           expnonevent = c('out1comp3time1expnon','out1comp3time2expnon','out1comp3time3expnon'),
                                           compevent = c( 'out1comp3time1compevent','out1comp3time2compevent','out1comp3time3compevent'),
                                           compnonevent = c( 'out1comp3time1compnon','out1comp3time2compnon','out1comp3time3compnon'),
                                           outage = c( 'es_out1comp3time1age','es_out1comp3time2age','es_out1comp3time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out1comp3.long1 <- out1comp3.long[ order( out1comp3.long$record_id, out1comp3.long$time ), ]
out1comp3.long1$comparison <- 3 
```

Merge all outcome 1 data frames together
```{r}
colnames( out1comp1.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')

colnames( out1comp2.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')

colnames( out1comp3.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')



out1varying <- rbind( out1comp1.long1, out1comp2.long1, out1comp3.long1 )

out1all <- merge( out1, out1varying, by = 'record_id', all.y = T )
```







# Outcome 2 preparation

Create outcome 2 data frame
```{r}
out2 <- df[, c( 1, 245:253, 255:294 ) ]
```

Create outcome 2, comparison 1 data frame
```{r}
out2comp1 <- df[, c( 1, 334:385 ) ]

out2comp1.long <- reshape( out2comp1,
                           varying = list( estype = c('out2comp1time1estype','out2comp1time2estype','out2comp1time3estype'),
                                           esdesc = c('out2comp1time1esdesc','out2comp1time2esdesc','out2comp1time3esdesc'),
                                           esmethod = c('out2comp1time1esmethod','out2comp1time2esmethod','out2comp1time3esmethod'),
                                           es = c('es_out2comp1time1','es_out2comp1time2','es_out2comp1time3'),
                                           es.se.report = c('es_se_report_o2c1t1','es_se_report_o2c1t2','es_se_report_o2c1t3'),
                                           es.se = c( 'es_se_o2c1t1','es_se_o2c1t2','es_se_o2c1t3'),
                                           n = c('es_out2comp1time1n','es_out2comp1time2n','es_out2comp1time3n'),
                                           expevent = c('out2comp1time1expevent','out2comp1time2expevent','out2comp1time3expevent'),
                                           expnonevent = c('out2comp1time1expnon','out2comp1time2expnon','out2comp1time3expnon'),
                                           compevent = c( 'out2comp1time1compevent','out2comp1time2compevent','out2comp1time3compevent'),
                                           compnonevent = c( 'out2comp1time1compnon','out2comp1time2compnon','out2comp1time3compnon'),
                                           outage = c( 'es_out2comp1time1age','es_out2comp1time2age','es_out2comp1time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out2comp1.long1 <- out2comp1.long[ order( out2comp1.long$record_id, out2comp1.long$time ), ]
out2comp1.long1$comparison <- 1        

```

Create outcome 1, comparison 2 data frame
```{r}
out2comp2 <- df[, c( 1, 387:438 ) ]

out2comp2.long <- reshape( out2comp2,
                           varying = list( estype = c('out2comp2time1estype','out2comp2time2estype','out2comp2time3estype'),
                                           esdesc = c('out2comp2time1esdesc','out2comp2time2esdesc','out2comp2time3esdesc'),
                                           esmethod = c('out2comp2time1esmethod','out2comp2time2esmethod','out2comp2time3esmethod'),
                                           es = c('es_out2comp2time1','es_out2comp2time2','es_out2comp2time3'),
                                           es.se.report = c('es_se_report_o2c2t1','es_se_report_o2c2t2','es_se_report_o2c2t3'),
                                           es.se = c( 'es_se_o2c2t1','es_se_o2c2t2','es_se_o2c2t3'),
                                           n = c('es_out2comp2time1n','es_out2comp2time2n','es_out2comp2time3n'),
                                           expevent = c('out2comp2time1expevent','out2comp2time2expevent','out2comp2time3expevent'),
                                           expnonevent = c('out2comp2time1expnon','out2comp2time2expnon','out2comp2time3expnon'),
                                           compevent = c( 'out2comp2time1compevent','out2comp2time2compevent','out2comp2time3compevent'),
                                           compnonevent = c( 'out2comp2time1compnon','out2comp2time2compnon','out2comp2time3compnon'),
                                           outage = c( 'es_out2comp2time1age','es_out2comp2time2age','es_out2comp2time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out2comp2.long1 <- out2comp2.long[ order( out2comp2.long$record_id, out2comp2.long$time ), ]
out2comp2.long1$comparison <- 2      
```

Create outcome 1, comparison 3 data frame
```{r}
out2comp3 <- df[, c( 1, 440:491 ) ]

out2comp3.long <- reshape( out2comp3,
                           varying = list( estype = c('out2comp3time1estype','out2comp3time2estype','out2comp3time3estype'),
                                           esdesc = c('out2comp3time1esdesc','out2comp3time2esdesc','out2comp3time3esdesc'),
                                           esmethod = c('out2comp3time1esmethod','out2comp3time2esmethod','out2comp3time3esmethod'),
                                           es = c('es_out2comp3time1','es_out2comp3time2','es_out2comp3time3'),
                                           es.se.report = c('es_se_report_o2c3t1','es_se_report_o2c3t2','es_se_report_o2c3t3'),
                                           es.se = c( 'es_se_o2c3t1','es_se_o2c3t2','es_se_o2c3t3'),
                                           n = c('es_out2comp3time1n','es_out2comp3time2n','es_out2comp3time3n'),
                                           expevent = c('out2comp3time1expevent','out2comp3time2expevent','out2comp3time3expevent'),
                                           expnonevent = c('out2comp3time1expnon','out2comp3time2expnon','out2comp3time3expnon'),
                                           compevent = c( 'out2comp3time1compevent','out2comp3time2compevent','out2comp3time3compevent'),
                                           compnonevent = c( 'out2comp3time1compnon','out2comp3time2compnon','out2comp3time3compnon'),
                                           outage = c( 'es_out2comp3time1age','es_out2comp3time2age','es_out2comp3time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out2comp3.long1 <- out2comp3.long[ order( out2comp3.long$record_id, out2comp3.long$time ), ]
out2comp3.long1$comparison <- 3 
```

Merge all outcome 1 data frames together
```{r}
colnames( out2comp1.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')

colnames( out2comp2.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')

colnames( out2comp3.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')



out2varying <- rbind( out2comp1.long1, out2comp2.long1, out2comp3.long1 )

out2all <- merge( out2, out2varying, by = 'record_id', all.y = T )
```









# Outcome 3 preparation

Create outcome 3 data frame
```{r}
out3 <- df[, c( 1, 493:501, 503:542 ) ]
```

Create outcome 3, comparison 1 data frame
```{r}
out3comp1 <- df[, c( 1, 582:633 ) ]

out3comp1.long <- reshape( out3comp1,
                           varying = list( estype = c('out3comp1time1estype','out3comp1time2estype','out3comp1time3estype'),
                                           esdesc = c('out3comp1time1esdesc','out3comp1time2esdesc','out3comp1time3esdesc'),
                                           esmethod = c('out3comp1time1esmethod','out3comp1time2esmethod','out3comp1time3esmethod'),
                                           es = c('es_out3comp1time1','es_out3comp1time2','es_out3comp1time3'),
                                           es.se.report = c('es_se_report_o3c1t1','es_se_report_o3c1t2','es_se_report_o3c1t3'),
                                           es.se = c( 'es_se_o3c1t1','es_se_o3c1t2','es_se_o3c1t3'),
                                           n = c('es_out3comp1time1n','es_out3comp1time2n','es_out3comp1time3n'),
                                           expevent = c('out3comp1time1expevent','out3comp1time2expevent','out3comp1time3expevent'),
                                           expnonevent = c('out3comp1time1expnon','out3comp1time2expnon','out3comp1time3expnon'),
                                           compevent = c( 'out3comp1time1compevent','out3comp1time2compevent','out3comp1time3compevent'),
                                           compnonevent = c( 'out3comp1time1compnon','out3comp1time2compnon','out3comp1time3compnon'),
                                           outage = c( 'es_out3comp1time1age','es_out3comp1time2age','es_out3comp1time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out3comp1.long1 <- out3comp1.long[ order( out3comp1.long$record_id, out3comp1.long$time ), ]
out3comp1.long1$comparison <- 1        

```

Create outcome 3, comparison 2 data frame
```{r}
out3comp2 <- df[, c( 1, 635:686 ) ]

out3comp2.long <- reshape( out3comp2,
                           varying = list( estype = c('out3comp2time1estype','out3comp2time2estype','out3comp2time3estype'),
                                           esdesc = c('out3comp2time1esdesc','out3comp2time2esdesc','out3comp2time3esdesc'),
                                           esmethod = c('out3comp2time1esmethod','out3comp2time2esmethod','out3comp2time3esmethod'),
                                           es = c('es_out3comp2time1','es_out3comp2time2','es_out3comp2time3'),
                                           es.se.report = c('es_se_report_o3c2t1','es_se_report_o3c2t2','es_se_report_o3c2t3'),
                                           es.se = c( 'es_se_o3c2t1','es_se_o3c2t2','es_se_o3c2t3'),
                                           n = c('es_out3comp2time1n','es_out3comp2time2n','es_out3comp2time3n'),
                                           expevent = c('out3comp2time1expevent','out3comp2time2expevent','out3comp2time3expevent'),
                                           expnonevent = c('out3comp2time1expnon','out3comp2time2expnon','out3comp2time3expnon'),
                                           compevent = c( 'out3comp2time1compevent','out3comp2time2compevent','out3comp2time3compevent'),
                                           compnonevent = c( 'out3comp2time1compnon','out3comp2time2compnon','out3comp2time3compnon'),
                                           outage = c( 'es_out3comp2time1age','es_out3comp2time2age','es_out3comp2time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out3comp2.long1 <- out3comp2.long[ order( out3comp2.long$record_id, out3comp2.long$time ), ]
out3comp2.long1$comparison <- 2      
```

Create outcome 1, comparison 3 data frame
```{r}
out3comp3 <- df[, c( 1, 688:739 ) ]

out3comp3.long <- reshape( out3comp3,
                           varying = list( estype = c('out3comp3time1estype','out3comp3time2estype','out3comp3time3estype'),
                                           esdesc = c('out3comp3time1esdesc','out3comp3time2esdesc','out3comp3time3esdesc'),
                                           esmethod = c('out3comp3time1esmethod','out3comp3time2esmethod','out3comp3time3esmethod'),
                                           es = c('es_out3comp3time1','es_out3comp3time2','es_out3comp3time3'),
                                           es.se.report = c('es_se_report_o3c3t1','es_se_report_o3c3t2','es_se_report_o3c3t3'),
                                           es.se = c( 'es_se_o3c3t1','es_se_o3c3t2','es_se_o3c3t3'),
                                           n = c('es_out3comp3time1n','es_out3comp3time2n','es_out3comp3time3n'),
                                           expevent = c('out3comp3time1expevent','out3comp3time2expevent','out3comp3time3expevent'),
                                           expnonevent = c('out3comp3time1expnon','out3comp3time2expnon','out3comp3time3expnon'),
                                           compevent = c( 'out3comp3time1compevent','out3comp3time2compevent','out3comp3time3compevent'),
                                           compnonevent = c( 'out3comp3time1compnon','out3comp3time2compnon','out3comp3time3compnon'),
                                           outage = c( 'es_out3comp3time1age','es_out3comp3time2age','es_out3comp3time3age') ),
                           v.names = c( 'estype','esdesc','esmethod','es','es.se.report','es.se','n','expevent','expnonevent','compevent','compnonevent','outage' ),
                           direction = 'long',
                           idvar = 'id',
                           times = 1:3 
                           )

out3comp3.long1 <- out3comp3.long[ order( out3comp3.long$record_id, out3comp3.long$time ), ]
out3comp3.long1$comparison <- 3 
```

Merge all outcome 1 data frames together
```{r}
colnames( out3comp1.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')

colnames( out3comp2.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')

colnames( out3comp3.long1 )[2:17] <- c('expdesc','expmeth___1','expmeth___2','expmeth___3','expmeth___4','expmeth___5',
                                       'exptype','exptime___1','exptime___2','exptime___3','exptimedesc','compdesc','type','time2needed',
                                       'time3needed')



out3varying <- rbind( out3comp1.long1, out3comp2.long1, out3comp3.long1 )

out3all <- merge( out3, out3varying, by = 'record_id', all.y = T )
```


# Combine all three outcomes
```{r}

vary <- setdiff( names( out1all ), names( out2all ) )

vary1 <- gsub("out1", "out", vary)

colnames(out1all)[colnames(out1all) %in% vary ] <- vary1


vary2 <- setdiff( names( out2all ), names( out3all ) )

colnames(out2all)[colnames(out2all) %in% vary2 ] <- vary1


vary3 <- setdiff( names( out3all ), names( out1all ) )

colnames(out3all)[colnames(out3all) %in% vary3 ] <- vary1


dfall <- rbind( out1all, out2all, out3all )

dfall[ dfall == -999 ] <- NA

#save( dfall, file = 'dfall.RData' )
```


